plot\_choro and shiny\_choro
----
The `plot_choro` and `shiny_choro` functions of `noncensus` provide an easy and
intuitive way to make basic choropleths and interactive choropleth shiny applications.

### Advantages

shiny_choro draws inspiration from the existing [rMaps](https://github.com/ramnathv/rMaps)
function ichoropleth by ramnathv while taking advantage of the existing Shiny 
leaflet bindings by [jcheng5](https://github.com/jcheng5/leaflet-shiny). noncensus' 
version is more flexible than ichoropleth, allowing a choice in map selection and 
choropleth color breaks.
At the same time, the average user does not need to have full knowledge of the
Shiny leaflet structure, and can easily get a functioning, interactive session
with just a one-line call. 

### An Example
The New York Times puts out nice interactives. One of the recent ones is shown 
[here](http://www.nytimes.com/2014/08/20/upshot/data-on-transfer-of-military-gear-to-police-departments.html?_r=0&abt=0002&abg=0). shiny_choro makes it easy to replicate this example, just using
R. 

We start with getting the raw data, conveniently provided on the NYT's github page
``` {r get_data, eval = FALSE}
library(dplyr)
library(stringr)
library(noncensus)

temp <- tempfile()
download.file(paste0("https://raw.githubusercontent.com/TheUpshot/Military-Surplus-Gear/",
                     "master/1033-program-foia-may-2014.csv"), 
              temp, method = "curl")
military <- tbl_df(read.csv(temp))
```

Now, the data are a bit messy, and we will need to supply the category labels ourselves.
There's a lot entries to go through, and since there is no consistent naming scheme, 
we'll do a quick and dirty assignment just on a few keywords. 

* Aircraft: "plane", "heli"
* Armoured vehicles: "atv", "vehicle" "truck"
* Body Armour: "armor", "armour", "helmet", "vest"
* Grenade Launchers: "launcher"
* Night vision: "night", "vision", "binocular", "sight", "goggle"  
* Assault rifle: "rifle"

``` {r add_labels, eval = FALSE}
military$category <- NA
military <- mutate(military, County = tolower(County), Item.Name = tolower(Item.Name))

gear_sort <- function(x){
  if(str_detect(x, "rifle")){
    return("Assault Rifles")
  } else if(str_detect(x, "night")| str_detect(x, "vision") | 
              str_detect(x, "binocular") | str_detect(x, "sight") | 
              str_detect(x, "goggle")){
    return("Night Vision")
  } else if(str_detect(x, "atv") | str_detect(x, "vehicle") | 
              str_detect(x, "truck")){
    return("Armoured Vehicles")
  } else if(str_detect(x, "plane") | str_detect(x, "heli")){
    return("Aircraft")
  } else if(str_detect(x, "launcher")){
    return("Grenade Launchers")
  } else if(str_detect(x, "armo[u]?r")| str_detect(x, "helmet") | 
              str_detect(x, "vest")){
    return("Body Armour")
  } else {
    return(NA)
  }
}

military$category <- sapply(military$Item.Name, gear_sort)
```

As of version 0.4, we need the FIPS code for each county in order to plot the data.
This can be achieved with two joins, one to get the full state name from its 
abbreviation, and one to add the FIPS code based on the full county name (given as
'state,county'). The two joining datasets are also from `noncensus`.

```{r add_fips, eval = FALSE}
data(states)
names(states)[1] <- "State"
military2 <- left_join(military, select(states, State, name), by = "State") %>% 
  select(-NSN)
military2$name <- tolower(military2$name)
military2$names <- apply(military2 %>% select(name, County), 1, paste, 
                         collapse = ",")

data(county_polygons)
military3 <- inner_join(military2, county_polygons %>% select(fips, names), 
                        by = "names")
military3 <- select(military3, Quantity, category, fips) %>% 
  filter(!is.na(category))
```

Now all that's left to do is aggregate all the entries into totals and call `shiny_choro`.

```{r shiny_call, eval = FALSE}
military3 <- military3 %>% group_by(fips, category) %>% 
  summarize(Quantity = sum(Quantity, na.rm = T))

shiny_choro(military3, fill = "Quantity", categories = "category", map = "county", 
            palette = "YlOrRd", background = "Grey")
```

### plot_choro
If we just want a static image for a composite or subset of the data, we can use
`plot_choro`, which works much in the same way as shiny_choro. For example, if we
want to look at just the overall quantity of items received (like the starting image
on the NYT page), we summarize, and call `plot_choro`.

```{r plot_call, eval = FALSE}
military4 <- military3 %>% summarize(Quantity = sum(Quantity, na.rm = T))

# show overall totals
plot_choro(military4, fill = "Quantity", map = "county", palette = "YlOrRd",
            background = "Grey")

# show just rifles
plot_choro(filter(military3, category == "Assault Rifles", fill = "Quantity", 
                  map = "county", palette = "YlOrRd", background = "Grey")
```

